Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
punctuation

Cells exhibit a dynamic volume-to-surface ratio in 
many physiological processes, such as 
cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell division~\cite{FredChang} and
apoptosis~\cite{marchetti1996mitochondrial}.
%osmotic flow across the membrane.
While osmotic stress  is more effective and efficient than mechanical stress in contributing to change in cellular volume, our results suggest that the water permeation due to the capillary pressure may be non-negligible over long times or under strong confinement in these physiological processes. Currently we are examining the combined effects of osmotic and mechanical stresses in the small Peclet number limit, which is relevant to cellular migration in the presence of both confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell} and has been studied numerically by Jaeger {\em et al.}~\cite{jae-car-med-try1999}

>>>>

Cells exhibit a dynamic volume-to-surface ratio in 
many physiological processes, such as 
cell migration in confined microenvironments~\cite{StrokaJiangChenEtAl2014_Cell, papadopoulos2008aquaporins}, 
dialysis~\cite{wan2006}, cell desiccation~\cite{vogl2014effect}, cell
division~\cite{FredChang}, and
apoptosis~\cite{marchetti1996mitochondrial}.
%osmotic flow across the membrane.
While osmotic stress  is more effective and efficient than mechanical
stress in contributing to change in cellular volume, our results suggest
that the water permeation due to the capillary pressure may be
non-negligible over long times or under strong confinement in these
physiological processes. Currently we are examining the combined effects
of osmotic and mechanical stresses in the small Peclet number limit,
which is relevant to cellular migration in the presence of both
confinement and a solute gradient~\cite{StrokaJiangChenEtAl2014_Cell}
and has been studied numerically by Jaeger {\em et
al.}~\cite{jae-car-med-try1999}.
